Bioverse: Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2024-11-21 src/tex/ms.tex
update lum/nuv plot and caption

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
%        \includegraphics[width=\hsize]{figures/hz_nuv_evo.bak.png}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} (right) as a function of host star mass.
        The scatter plots show age and host star mass of the transiting planets in the synthetic FGK sample; crosses denote the estimated \gls{NUV} values in \citet{Richey-Yowell2019}. % with \gls{EEC} highlighted in green.
        A few example tracks for an example threshold flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$ are shown; extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections) fulfills our requirement for abiogenesis.
        Planet~1 is an \gls{EEC} that never receives sufficient \gls{NUV} flux for abiogenesis.
        Planet~2 and Planet~3 enter the \gls{HZ} at different times and receive sufficient \gls{NUV} flux for different durations until their respective host star evolves below the threshold.
        }
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

>>>>

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
%        \includegraphics[width=\hsize]{figures/hz_nuv_evo.bak.png}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} (right) as a function of host star mass.
        Scatter points show age and host star mass of the transiting planets in the synthetic planet sample; crosses denote the estimated \gls{NUV} values in \citet{Richey-Yowell2019}. % with \gls{EEC} highlighted in green.
        We show three evolutionary tracks for a threshold flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\erg\per\second\per\centi\meter\squared}$ that occupy the \gls{HZ} (green sections) and exceed the threshold \gls{NUV} flux (blue sections) at different times.
        Where these sections overlap (orange rectangles), the requirements for abiogenesis are met and we assign a biosignature detection with probability $f_\mathrm{life}$.
        Planet~1 is an \gls{EEC} orbiting a K~dwarf that never receives sufficient \gls{NUV} flux for abiogenesis.
        Planet~2 and Planet~3 enter the \gls{HZ} at different times and receive sufficient \gls{NUV} flux for different durations until their respective host star evolves below the threshold.
        }
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}
